Analysis paper

### 2021-06-02 analysis/analysis.Rmd
add table with sd and median of wis

  setcolorder(scores, 
              neworder = c("Target", "Horizon", "Model", "WIS"))

@@

>>>>

  if ("WIS" %in% names(scores)) {
    setcolorder(scores, 
                neworder = c("Target", "Horizon", "Model", "WIS"))  
  }

@@

```{r}
# calculate median and sd of the WIS -------------------------------------------

df <- eval_forecasts(
  filtered_data, 
  metric = "interval_score",
  summarise_by = c("model", "horizon", "target_type"), 
  sd = TRUE, 
  quantile = 0.5
)

df <- df[, .(model, horizon, target_type, 
             `WIS - mean` = interval_score, 
             `WIS - median` = interval_score_0.5, 
             `WIS - sd` = interval_score_sd)] %>%
    dcast(... ~ ., value.var = c("WIS - mean", "WIS - median", "WIS - sd"))

setcolorder(df, c("target_type", "horizon", "model"))

table <- df[order(target_type, horizon, model)] %>%
  make_score_table()

save_kable(table, 
           file = here("analysis", "plots", "table-wis-sd-median.png"))
